---
title: "Analysing historical voting of the United Nations General Assembly"
author: "Utkarsh Sharma"
date: "16/09/2019"
output: 
  prettydoc::html_pretty:
    toc: true
---

# Analysing historical voting of the United Nations General Assembly

The [dataset](https://dataverse.harvard.edu/api/access/datafile/:persistentId?persistentId=doi:10.7910/DVN/LEJUQZ/KKG7SW) contains the historical voting data from the General Assembly of the United Nations. This is a dataset of roll-call votes in the UN General Assembly 1946-2018. In the General Assembly, every member nation gets a vote, which makes the voting history a great resource to study international relations.

The raw data was sourced from the Harvard Dataverse. 

*Citation: Voeten, Erik; Strezhnev, Anton; Bailey, Michael, 2009, "UN-73new.RData", United Nations General Assembly Voting Data, https://doi.org/10.7910/DVN/LEJUQZ/KKG7SW, Harvard Dataverse, V21*

```{r message = FALSE}
#Importing and installing required libraries
library(dplyr)
library(ggplot2)

# Loading dataset
load("~/Desktop/Analysing historical voting of the United Nations General Assembly/Dataset/UN-73new.RData")
```

Checking out the first six rows of the dataset.
```{r warning = FALSE}
  head(completeVotes)
```

The vote column in the dataset has a number that represents that country's vote:

1 = Yes, 2 = Abstain, 3 = No, 8 = Not present, 9 = Not a member

To study the international relationships between countries, we filter out the result with voting results 'Not present' and 'Not a member'.

```{r}
  filteredVotes <- completeVotes %>% 
                  filter(vote %in% c("1", "2", "3"))
```

## Year-over-year consensus

To find the year-by-year overall trend of voting against or for the international consensus, we plot the year-by-year percentage of "Yes" votes.

```{r warning = FALSE}
  year_by_yearYes <- filteredVotes %>% 
                    group_by(year) %>% 
                    summarize(PercentageofYes = mean(vote == 1) * 100)

  years <- c("1946", "1950", "1960", "1970", "1980", "1990", "2000", "2010", "2018")

  ggplot(year_by_yearYes, aes(year, PercentageofYes, group = 1)) + geom_line() + xlim(years) 
```

Here, it can be easily seen that the overall consensus has greatly improved since 1960.

## Country consensus

If a country tends to votes "Yes" on most occassions, it can be inferred that it tends to agree with the international consensus, while if it votes "No" on most occassions, it can be assumed that it tends to go against the consensus. 

```{r}
  byCountryYes <- filteredVotes %>% 
                  group_by(Countryname) %>% 
                  summarize(Votes = n(), PercentageofYes = mean(vote == 1) * 100)

  head(byCountryYes %>% arrange(PercentageofYes))
```

It can be seen that the country Zanzibar only has 2 votes casted in the General Assembly. To get a clearer picture, we filter out country with low number of votes.

```{r}
  head(byCountryYes %>% filter(Votes > 200) %>% arrange(desc(PercentageofYes)))
```

