---
title: "Analysing historical voting of the United Nations General Assembly"
author: "Utkarsh Sharma"
date: "16/09/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysing historical voting of the United Nations General Assembly

The [dataset](https://dataverse.harvard.edu/api/access/datafile/:persistentId?persistentId=doi:10.7910/DVN/LEJUQZ/KKG7SW) contains the historical voting data from the General Assembly of the United Nations. This is a dataset of roll-call votes in the UN General Assembly 1946-2018. In the General Assembly, every member nation gets a vote, which makes the voting history a great resource to study international relations.

The raw data was sourced from the Harvard Dataverse. 

*Citation: Voeten, Erik; Strezhnev, Anton; Bailey, Michael, 2009, "UN-73new.RData", United Nations General Assembly Voting Data, https://doi.org/10.7910/DVN/LEJUQZ/KKG7SW, Harvard Dataverse, V21*

```{r message = false}
#Importing and installing required libraries
library(dplyr)
library(ggplot2)

# Loading dataset
load("~/Desktop/Analysing historical voting of the United Nations General Assembly/Dataset/UN-73new.RData")
```




